### 2018-03-11 paper/3-compute.tex
Avoid specific function names in the vocabulary

A \emph{store} associates keys to values. It is convenient to assume that a
store is total function \store, i.e. it contains a value for every possible key.
We therefore also assume that the type of values is capable of encoding values
corresponding to non-existent keys (missing files or empty cells). This, in
particular, suggests that it is possible to \emph{depend on the absence of a
value}, which is a useful feature for build systems. In addition to usual
\hs{get} and \hs{put} operations, some stores support the \hs{getHash} operation
implemented more efficiently than by hashing the result of \hs{get}. For example,
GVFS (Git Virtual File System)~\cite{gvfs} stores file hashes and downloads file
contents only on demand -- an important feature for cloud build systems.

>>>>

A \emph{store} associates keys to values. It is convenient to assume that a
store is total function \store, i.e. it contains a value for every possible key.
We therefore also assume that the type of values is capable of encoding values
corresponding to non-existent keys (missing files or empty cells). This, in
particular, suggests that it is possible to \emph{depend on the absence of a
value}, which is a useful feature for build systems. In addition to usual
read and write operations, some stores also support a dedicated \emph{read hash}
operation, which is implemented more efficiently than by reading and hashing the
result. For example, GVFS (Git Virtual File System)~\cite{gvfs} stores file
hashes and downloads file contents only on demand -- an important feature for
cloud build systems.
